---
title: "Crossmodal - instruction file"
author: "Laura Bock Paulsen - edits Sara Kristensen"
date: "9/9/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE) 
setwd('.')
```

```{r}
pacman::p_load(tidyverse, readbulk, patchwork, lmerTest)
```

For this class, the aim is to investigate some cross modal effects. This will be done using the data from the experiment you **hopefully** completed before today's class.

There are 4 steps to today's exercise: 

1) Load in data
2) Investigation and preparation of the data
3) Investigate if congruency predicts reaction time using linear regression
4) Visualization of accuracy rate


Enjoy!

## Load in data

### Download data
First of all, you need to download the data from the Google drive folder: **https://drive.google.com/drive/folders/19HsBvrrnRynsn0z90iZhqL5SRaj-nnlw?usp=sharing** or just skip to the next step if you cloned the GitHub repo (data should be included).

### Load data
Load in the data.
```{r}
aud <- read_bulk(
  directory = 'data_aud/',
  fun = read_csv,
  col_types = cols()  # suppresses the annoying column specifications (not needed to run)
  )

vis <- read_bulk(
  directory = 'data_vis/',
  fun = read_csv,
  col_types = cols()
  )

head(aud)
```

Hint: you can use read_bulk() from the readbulk package to load the different csv files into one dataframe (one df for vision, one for audition). 


### Discussion
Before you start looking at the data, discuss what predictions you have and why.
- Prediction when the participants fail the reaction time is slower for the next trial, due to the risk of mistaken
- The accuracy is lower for incongruent stimuli trials.
- Does attention matter for the accuracy for the congruency stimuli in the two experiment? Visual versus auditory attention


# Investigation and preperation of the data

### Data structure
To begin with try to get an overview of the data by answering the following questions:

What variables do we have? 
```{r}
pacman::p_load(janitor)
compare_df_cols(aud,vis)
vis$version <- recode(vis$version,'auditory'='vision')
```

Which variables are we interested in? 
- reaction time
- congruency
- accuracy
- subject
- time_elapsed

Are the variables in the right format (e.g., factor, numeric)? If they are not, make sure they are.
```{r}
vis$subject <- as.factor(vis$subject)
vis$congruency <- as.factor(vis$congruency)
aud$subject <- as.factor(aud$subject)
aud$congruency <- as.factor(aud$congruency)

compare_df_cols(vis,aud)
```

How many participants do we have in each condition?
```{r}
length(unique(vis$subject))
length(unique(aud$subject))
#16 versus 16
```


Create new dataframes that only contains the correct trials. The dataframes with both correct and incorrect trials will be used in the last part of the exercise, so do not overwrite this. 
```{r}
viscor <- subset(vis,accuracy=='TRUE')
audcor <- subset(aud,accuracy=='TRUE')
```


### Initial plot
To further look into the data, lets make a quick plot! More specifically, make a plot of the mean reaction time per concurrency. Make sure to include errorbars. 

```{r}

```

### Discussion
Interpret the findings. Do they match your predictions? Why? Why not? 


# Investigate if congruency predicts reaction time using a linear model
Does congruency predict the reaction time? Lets find out. 

To do this, make a simple linear model. 
```{r}

```

### Report the results
Imagine this was your exam project. What would you write in the results section? Write a sentence or two reporting the results of the two linear models (APA style).


# Visuallisation of accuracy rate
Make a graph of the accuracy rate. Is there a way to visualize the relationship between congruency and the percentage of incorrectly answered trials per subject?
```{r}

```

Hint: Which data frames contain both correct and incorrect trials?

### Discussion
Discuss the resulting plots. 


## Optional (If you are done before time is up)
Earlier you created a simple linear model to test if congruency predicted the reaction time. Are there other **Cough chough** bayesian **Cough cough** ways to investigate this? If so, give it a go!


