---
title: "Mousetracking Analysis"
author: "Laura Bock Paulsen"
date: "9/11/2022"
output: html_document
---

For the analysis of your very own mouse-tracking data, we will be using a package called MouseTrap. In order to get acquainted with the package, we will play around with data from a single participant conduction the circle-square experiment. 

The documentation for the package can be found here: <https://www.rdocumentation.org/packages/mousetrap/versions/3.1.5/topics/mousetrap>.

Use this page to solve the following steps by finding and applying appropriate mousetrap functions. Also, writing ?function_name() in the console is great way of reading about the function in question.

<<<<<<< HEAD
Call me for help whenever you get stuck (or take a quick look in the solutions file) :-)
=======
Call me for help whenever you get stuck (or take a quick look in the solutions file) :D
>>>>>>> 451bec789a2e73428b2797bb8af1297cd068bc5a

### Install packages and load in the data
```{r}
# loading packages
<<<<<<< HEAD
pacman::p_load(mousetrap, tidyverse, ggplot2, gridExtra)

# loading in data
d <- read.csv('example_data/subject-98.csv')
d3 <- read.csv('example_data/subject-3.csv')
=======
pacman::p_load(mousetrap, tidyverse)

# loading in data
d <- read_csv('example_data/subject-3.csv')
>>>>>>> 451bec789a2e73428b2797bb8af1297cd068bc5a
```

### Turn the data into a mousetrap object
```{r}
<<<<<<< HEAD
m <- mousetrap::mt_import_mousetrap(d)
m3<- mousetrap::mt_import_mousetrap(d3)
=======
m <- mt_import_mousetrap(d)
>>>>>>> 451bec789a2e73428b2797bb8af1297cd068bc5a
```
Take a moment to look at the structure that it created. What are the elements, what information does it provide?

### Make a quick plot using the mt_plot() function
Try to understand what the lines mean and how to “read” the graph. What seems weird about it when you think about how the experiment task looked like?
```{r}
# initial plot
mt_plot(m)
<<<<<<< HEAD
mt_plot(m3)
=======
>>>>>>> 451bec789a2e73428b2797bb8af1297cd068bc5a

# specified
mt_plot(data = m, use = 'trajectories')
```

### Make a plot in which the lines are coloured by condition
The demo-experiment had different trial types for which we have different predictions. Make a plot that distinguishes these two conditions, e.g. by different colors. 
```{r}
mt_plot(m, color = 'trial_type')
<<<<<<< HEAD
mt_plot(m3,color='trial_type')
=======
>>>>>>> 451bec789a2e73428b2797bb8af1297cd068bc5a
```


### Mirror-symmetric mapping of movements
Find a function that does a mirror-symmetric mapping of all the movements from the right side to the left side so that all movements overlap. Plot again. What does this function also do?
```{r}
# align the mouse trajectories to one side
m <- mt_remap_symmetric(
  m, 
  use = 'trajectories',
  remap_xpos = "left"
  )

# plot again
mt_plot(
  m, 
  use = 'trajectories',
  color = 'trial_type'
  )

# turns the data upside down, so it resembles the actual mouse tracking task
<<<<<<< HEAD

# align the mouse trajectories to one side
m3 <- mt_remap_symmetric(
  m3, 
  use = 'trajectories',
  remap_xpos = "left"
  )

# plot again
mt_plot(
  m3, 
  use = 'trajectories',
  color = 'trial_type'
  )
=======
>>>>>>> 451bec789a2e73428b2797bb8af1297cd068bc5a
```

### Plot timestamps by xpos
The standard plotting function shows x and y coordinates. Modify it so you plot timestamps by xpos. What do you see? What is this line in the beginning?
```{r}
<<<<<<< HEAD
a <- mt_plot(
=======
mt_plot(
>>>>>>> 451bec789a2e73428b2797bb8af1297cd068bc5a
  m, 
  x = 'timestamps', # modifying the x-axis to plot timestamps
  y = 'xpos',       # modifying the y-axis to plot the xpos
  use = 'trajectories',
  color = 'trial_type' 
)
<<<<<<< HEAD

b <- mt_plot(
  m3, 
  x = 'timestamps', # modifying the x-axis to plot timestamps
  y = 'xpos',       # modifying the y-axis to plot the xpos
  use = 'trajectories',
  color = 'trial_type' 
)

ab <- gridExtra::grid.arrange(a,b)
=======
>>>>>>> 451bec789a2e73428b2797bb8af1297cd068bc5a
```

### Find a function that removes the initial phase without mouse-movement
Find a function to remove this “line”.

```{r}
m <- mt_exclude_initiation(m)
<<<<<<< HEAD
m3 <- mt_exclude_initiation(m3)
=======
>>>>>>> 451bec789a2e73428b2797bb8af1297cd068bc5a
```

Before plotting again (timestamps and xpos) think about how you expect it to look. Then plot it, to see if you were right.
```{r}
<<<<<<< HEAD
c <- mt_plot(
=======
mt_plot(
>>>>>>> 451bec789a2e73428b2797bb8af1297cd068bc5a
  m, 
  x = 'timestamps', # modifying the x-axis to plot timestamps
  y = 'xpos',       # modifying the y-axis to plot the xpos
  use = 'trajectories',
  color = 'trial_type' 
)
<<<<<<< HEAD
d <- mt_plot(
  m3, 
  x = 'timestamps', # modifying the x-axis to plot timestamps
  y = 'xpos',       # modifying the y-axis to plot the xpos
  use = 'trajectories',
  color = 'trial_type' 
)
grid.arrange(c,d,a,b,nrow=2)
=======
>>>>>>> 451bec789a2e73428b2797bb8af1297cd068bc5a
```


### Time-normalize the data
Apply the function “mt_time_normalize”
```{r}
m <- mt_time_normalize(m)
<<<<<<< HEAD
m3 <- mt_time_normalize(m3)
=======
>>>>>>> 451bec789a2e73428b2797bb8af1297cd068bc5a
```

Now look at your data variable (the mt object) where a new matrix appeared. What do you notice? What does the function do? After you have thought about it yourself, check the documentation!


### Plot the normalized trajectories
Find out how to plot the normalized trajectories instead of the raw data.
```{r}
mt_plot(
  m, 
  use = 'tn_trajectories',
  color = 'trial_type'
)
```


### Play around with the mt_time_normalize() function
Take a moment to play around with different numbers of steps in “mt_time_normalize” and see how that changes the shape of the trajectories, esp. when using very small numbers. Discuss what the decision about normalizing implies for the data analysis and interpretation. In the end, set the steps back to the default of 101.
```{r}
<<<<<<< HEAD
#100
m_tn <- mt_time_normalize(
  m,
  nsteps = 100
)

#plot
hun <- mt_plot(
  m_tn, 
  use = 'tn_trajectories',
  color = 'trial_type'
)+ggplot2::ggtitle('100')

#10
m_tn <- mt_time_normalize(
  m,
  nsteps = 10
)

#plot
ten <- mt_plot(
  m_tn, 
  use = 'tn_trajectories',
  color = 'trial_type'
)+ggplot2::ggtitle('10')

#50
m_tn <- mt_time_normalize(
  m,
  nsteps = 50
)

#plot
fiveten <- mt_plot(
  m_tn, 
  use = 'tn_trajectories',
  color = 'trial_type'
)+ggplot2::ggtitle('50')

grid.arrange(ten,fiveten,hun,nrow=2)
```

=======
m_tn <- mt_time_normalize(
  m,
  nsteps = 101
)

#plot
mt_plot(
  m_tn, 
  use = 'tn_trajectories',
  color = 'trial_type'
)
```


>>>>>>> 451bec789a2e73428b2797bb8af1297cd068bc5a
### Aggregated plots
Now we want to visualize our “findings”. Find a function that will plot averages of all the “similar” movements and all the “dissimilar” movements.
Think: Which trajectories do we need to use, the original or the time normalized? Why? Try plotting both to see whether you were right.
```{r}
<<<<<<< HEAD
e <- mt_plot_aggregate(
  m, 
  use = 'trajectories',
  color = 'trial_type'
)+ggplot2::ggtitle('Aggregated mouse trajectories')

f <- mt_plot_aggregate(
  m_tn, 
  use = 'tn_trajectories',
  color = 'trial_type'
) + 
    ggplot2::ggtitle('Aggregated time-normalized mouse trajectories')

grid.arrange(e,f)
=======
mt_plot_aggregate(
  m, 
  use = 'trajectories',
  color = 'trial_type'
)

mt_plot_aggregate(
  m, 
  use = 'tn_trajectories',
  color = 'trial_type'
) + 
  labs(
    title = 'Aggregated time-normalized mouse trajectories')
>>>>>>> 451bec789a2e73428b2797bb8af1297cd068bc5a
```


### Apply the function mt_measures()
Apply the function “mt_measures” and look at the outcome in your data variable. 
```{r}
m <- mt_measures(m, use = 'tn_trajectories')
<<<<<<< HEAD
m3 <- mt_measures(m3, use = 'tn_trajectories')
=======
>>>>>>> 451bec789a2e73428b2797bb8af1297cd068bc5a
```

### Aggregating measures
Now find a function that helps you aggregate some measures of your pleasing over the two trial_types.
```{r}
<<<<<<< HEAD
mt3_measures_ag <- mt_aggregate(
  m3,
  use = 'measures',
  use_variables = c('MAD', 'xpos_flips','AUC', 'RT'), # if you want all of the measures, exclude this line
  use2_variables = 'trial_type'
  )

=======
>>>>>>> 451bec789a2e73428b2797bb8af1297cd068bc5a
mt_measures_ag <- mt_aggregate(
  m,
  use = 'measures',
  use_variables = c('MAD', 'xpos_flips','AUC', 'RT'), # if you want all of the measures, exclude this line
  use2_variables = 'trial_type'
  )

mt_measures_ag
```


### Interpret the results
Take a moment to think what these “results” could mean if this was a proper experiment which was not run by your instructor. How would you interpret this? Does this match your hypothesis? Especially look at the MAD (maximum absolute deviation from the direct path), the AUC (area under the curve) and the reaction time. 
<<<<<<< HEAD
```{r}
#test's for laura
m_mea3 <- as.data.frame(m3$measures)
m_mad_auc3 <- subset(m_mea3,select=c(MAD,AUC,RT))
m_data <- as.data.frame(m3$data)
m_data_trial <- subset(m_data,select=c(trial_type))
use3 <- merge(m_data_trial,m_mad_auc3)
auc3 <- t.test(AUC~trial_type,data=use3) 
MAD3 <- t.test(MAD~trial_type,data=use3) 
rt3 <- t.test(RT~trial_type,data=use3) 

#test's for sara
m_mea <- as.data.frame(m$measures)
m_mad_auc <- subset(m_mea,select=c(MAD,AUC,RT))
m_data <- as.data.frame(m$data)
m_data_trial <- subset(m_data,select=c(trial_type))
use <- merge(m_data_trial,m_mad_auc)
auc <- t.test(AUC~trial_type,data=use) 
MAD <- t.test(MAD~trial_type,data=use) 
rt <- t.test(RT~trial_type,data=use) 

# tests together
use3 <- use3 %>% 
  mutate(ID='3')
use <- use %>% 
  mutate(ID="98")
USE <- rbind(use,use3)
auct <- t.test(AUC~trial_type,data=USE) 
MADt <- t.test(MAD~trial_type,data=USE) 
rtt <- t.test(RT~trial_type,data=USE) 


#bind results together
sara <- rbind(rt,auc,MAD)
laura <- rbind(rt3,auc3,MAD3)
uset <- rbind(rtt,auct,MADt)
Trial_type <- c('RT','AUC','MAD','RT3','AUC3','MAD3','RT_T','AUC_T','MAD_T')
tt <- rbind(sara,laura,uset)
tt <- data.frame(Trial_type,tt)
rownmaes <- rownames(tt)
rownames(tt) <- c('RT','AUC','MAD','RT3','AUC3','MAD3','RT_T','AUC_T','MAD_T')

#make table to compare subjects
ttt <- table(tt$Trial_type,tt$p.value)
names(dimnames(ttt)) <- c("Participant(s)", "P-value")
names(dimnames(ttt))
ttt
```
### Answer: no difference between trials nor participants... a bit weird but okay.
=======

>>>>>>> 451bec789a2e73428b2797bb8af1297cd068bc5a


## Additional exercises

### Removing incorrect trials
Normally, you'd want to remove incorrect trials. As the mouse_trap object does not function with tidyverse, figure out how to remove potential incorrect trials from your mousetrap object. 
```{r}
m <- mt_subset(
  m,
  correct == '1'
)
```

### Discussion of mt_align
Would the function ‘mt_align’ be useful for this data? Why or why not?
<<<<<<< HEAD
- Nice to lay the trajectories accurately on top of each other, since the experiment is designed to place the mouse in the same starting position every time.

=======
>>>>>>> 451bec789a2e73428b2797bb8af1297cd068bc5a
It can do the same as mt_remap symmetric, but it can also be used to rescale (here 'space-normalize') the data. 

You could align the starting and end position, as we are only interested in the trajectory of the mouse movement, not the endpoint in it self. Also, because the end point could be anywhere within the stimulus (circle or square), it looks nice to drag the trajectories to the same point. 

As we only have one participant, I wouldn't say it is necessary (or beneficial, besides it looks nice). 

```{r}
# an example of aligning the data
m_align <- mt_align(
  m,
  use = 'trajectories',
  dimensions = c("xpos", "ypos"),
  coordinates = c(0,0,-350,250),
  align_start = T,
  align_end = T
)
  
  # plot again
mt_plot(
  m_align, 
  use = 'trajectories',
)
<<<<<<< HEAD
```
=======
```

### ggplot
As the mt_plot function uses ggplot, you can easily add themes, titles and such to make your plots look nice. Have a go at it!
```{r}
mt_plot(
  m_align, 
  use = 'trajectories',
  color = 'trial_type'
) + 
  theme_minimal() +
  labs(title = 'Alligned mouse-tracking data', x = 'Postition (x)', y = 'Postistion(y)', color = 'Trial Type')
```


>>>>>>> 451bec789a2e73428b2797bb8af1297cd068bc5a
